Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-10-27 paper/main.tex
Fixed typos

\subsection{NIST SHA-3 Competition}
The \ac{SHA} version 3 is a comming standard set to superceed the current
standards \ac{SHA}-1 and \ac{SHA}-2 families. The hash function to become
\ac{SHA}-3 will be decided by \ac{NIST} and choosen between the submitted
contestants to the \ac{NIST} hash competition. The current status of the 
competition is officially called Round 2, with 14 of 64 candidates having 
survived round 1\cite{s_fedreg}.

@@

\paragraph{Security} is the most important criteria for the SHA-3
candidates\cite{s_nistround2}. The full description of security criterias are
mentioned in \cite{s_fedreg}, however the most noteworthy criteria in regards
to Tahoe-\ac{LAFS} is that \ac{SHA}-3 candidates are required to have
resistance against length-extension attacks. Length-extension attacks is
something that both \ac{SHA}-1 and the \ac{SHA2}-family suffers
from\cite{s_mdre}.

>>>>

\subsection{NIST SHA-3 Competition}
The \ac{SHA} version 3 is a comming standard set to superceed the current
standards \ac{SHA}-1 and the \ac{SHA}-2 family. The hash function to become
\ac{SHA}-3 will be decided by \ac{NIST} and choosen between the submitted
contestants to the \ac{NIST} hash competition. The current status of the 
competition is officially called Round 2, with 14 of 64 candidates having 
survived round 1\cite{s_fedreg}.

@@

\paragraph{Security} is the most important criteria for the SHA-3
candidates\cite{s_nistround2}. The full description of security criterias are
mentioned in \cite{s_fedreg}, however the most noteworthy criteria in regards
to Tahoe-\ac{LAFS} is that \ac{SHA}-3 candidates are required to have
resistance against length-extension attacks. Both \ac{SHA}-1 and the \ac{SHA}-2
family are vulnerable to this attack\cite{s_mdre}.
